Turbulence in compact to giant HII regions

### 2022-06-28 strucfunc_paper.tex
Updates from Overleaf

%Luminosity vs centroid velocity dispersion
The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
In our case if taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6}\). 
Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
The fact that this relation

>>>>

%Luminosity vs centroid velocity dispersion
The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
In our case if taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6}\). 
Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) theoretical relation.
The fact that this relationship holds in our results is of importance considering that the \(\sigma\pos\) is obtained using the structure function.
This means that the proposed model describes
